The candidate confirms that the work submitted is his own, except where work which has formed part of jointly authored publications has been included. The contribution of the candidate and the other authors to this work has been explicitly indicated below. The candidate confirms that appropriate credit has been given within the thesis where reference has been made to the work of others.

Two publications have arisen from the work presented in this thesis, both from work detailed in Chapter~4:

\textbf{C. N. A. Towler}, J. Kendrick, and A. D. Burnett, “Understanding the effect of dispersion corrections on the calculated spectra of \(\alpha\)\nobreakdash-lactose monohydrate,” in \textit{2020 45th International Conference on Infrared, Millimeter, and Terahertz Waves (IRMMW\nobreakdash-THz)}, 2020, pp. 1\nobreakdash–2. 25

\vspace{0.1cm}

The time\nobreakdash-domain spectroscopy system used to measure the terahertz absorption spectrum at \SI{4}{K} was originally designed by Dr. Andrew Burnett. The software used to produce terahertz absorption spectra from calculated mode frequencies and intensities was written by Dr. John Kendrick. I collected all the data, produced all the figures and wrote the initial and final drafts of this paper, with all authors contributing between these drafts.

\vspace{0.7cm}

A. D. Burnett, \textbf{C. N. A. Towler}, and J. Kendrick, “Calculating the complex permittivity of powdered crystalline materials,” in \textit{2019 44th International Conference on Infrared, Millimeter, and Terahertz Waves (IRMMW\nobreakdash-THz)}, 2019, pp. 1–2. 9

\vspace{0.1cm}

I produced the data and designed the figure for the comparison of the calculated and experimental terahertz absorption spectra of \(\alpha\)\nobreakdash-Lactose Monohydrate. No other contribution to this work occurred.

This copy has been supplied on the understanding that it is copyright material and that no quotation from the thesis may be published without proper acknowledgement.

The right of Calum Neil Alasdair Towler to be identified as Author of this work has been asserted by Calum Neil Alasdair Towler in accordance with the Copyright, Designs and Patents Act 1988.


